Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-17 tex/paper1/paper1.tex
edits to the paper, and to the prep program to cheaply get the physical extent of the data

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is ??? to ??? in the x-direction, and ??? - ??? in the
  y-direction, in heliocentric cartesian co-ordinates
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

In order to perform the fit, the noise in the \mFps\ must be
estimated.  To do that, the power distributions of Section \ref{???}
are considered.  The Fourier power at a given pixel is not independent
of the Fourier power at another pixel.  This is because neighbouring
pixels are highly likely to be physically connected to each other, and
so time-series in neighboring pixels are likely to be strongly
correlated (assuming that the background structure exists over at
least two pixels).  Also, the point spread function of AIA spreads
emission in one pixel over on to its neighbors.  Secondly, the
distributions are only approximately normal.

>>>>

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

In order to perform the fit, the noise in the \mFps\ must be
estimated.  To do that, the power distributions of Section
\ref{sec:anal} are considered.  The Fourier power at a given pixel is
not independent of the Fourier power at another pixel.  This is
because neighbouring pixels are highly likely to be physically
connected to each other, and so time-series in neighboring pixels are
likely to be strongly correlated (assuming that the background
structure exists over at least two pixels).  Also, the point spread
function of AIA spreads emission in one pixel over on to its
neighbors.  Secondly, the distributions are only approximately normal.
